\break
\section{Legal}
\subsection{License}
Copyright 2019 Luuk Willemsen

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

\subsection{Laws and regulations}
This project is published as free software (see license section above) under a MIT license (or similar).

Since this is a software-only project, the above license covers all legal use of the software, and explicitly waives all liability and possible claims for the author. Users are responsible for any use of the software.


\section{Technical skills}
The technical skills that are considered relevant in this projects are the following, as per the project's initial presentation:

\begin{itemize}
    \item \textbf{CCO1.1}: 
    Evaluate the computational complexity of a problem, learn algorithmic strategies that can lead to its resolution, and recommend, develop and implement the one that guarantees the best performance in accordance with the established requirements. 
    \item \textbf{CCO2.3} Develop and evaluate interactive and complex information presentation systems, and their application to solving computer interaction design problems.
    \item \textbf{CCO2.6} Design and implement graphics, virtual reality, augmented reality and video games applications.
\end{itemize}

